\mytitle

### 2012-02-21 papers/SAS2012/implicitization.tex
On cite le nom de l'outil (PAGAI) maintenant que c'est plus anonyme

We have implemented our proposed solutions inside a prototype of intraprocedural
static analyzer,
as well as the classical abstract interpretation algorithm, and the state-of-the-art
techniques \emph{Path Focusing} \cite{Monniaux_Gonnord_SAS11} and \emph{Guided
Static Analysis} \cite{DBLP:conf/sas/GopanR07}.

%\MM{On peut peut-être citer le nom de l'outil (on garde PAGAI ?) ici.
%  L'intérêt d'avoir un nom, c'est que les gens peuvent en parler plus
%  facilement, et c'est plus facile de retrouver le papier origine d'un
%  outil quand il cite son nom}
%\DM{Dans la version finale, oui, mais pas dans une soumission anonymisée... suffit de Googlifier pagai sur imag.fr}
%
Our tool operates over LLVM bitcode \cite{LLVM_langref,Lattner:2004:LCF:977395.977673}, which is a target for several compilers, most notably Clang (supporting C and C++) and llvm-gcc (supporting C, C++, Fortran and Ada).
Abstract domains are provided by the APRON library \cite{DBLP:conf/cav/JeannetM09}, and include convex polyhedra (from the builtin Polka ``PK'' library), octagons, intervals, and linear congruences.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3~\cite{DBLP:conf/tacas/MouraB08}.

>>>>

We have implemented our proposed solutions inside a prototype of intraprocedural
static analyzer called PAGAI,
as well as the classical abstract interpretation algorithm, and the state-of-the-art
techniques \emph{Path Focusing} \cite{Monniaux_Gonnord_SAS11} and \emph{Guided
Static Analysis} \cite{DBLP:conf/sas/GopanR07}.

%\MM{On peut peut-être citer le nom de l'outil (on garde PAGAI ?) ici.
%  L'intérêt d'avoir un nom, c'est que les gens peuvent en parler plus
%  facilement, et c'est plus facile de retrouver le papier origine d'un
%  outil quand il cite son nom}
%\DM{Dans la version finale, oui, mais pas dans une soumission anonymisée... suffit de Googlifier pagai sur imag.fr}
%
PAGAI operates over LLVM bitcode \cite{LLVM_langref,Lattner:2004:LCF:977395.977673}, which is a target for several compilers, most notably Clang (supporting C and C++) and llvm-gcc (supporting C, C++, Fortran and Ada).
Abstract domains are provided by the APRON library \cite{DBLP:conf/cav/JeannetM09}, and include convex polyhedra (from the builtin Polka ``PK'' library), octagons, intervals, and linear congruences.
For SMT-solving, our analyzer uses Yices
\cite{DBLP:conf/cav/DutertreM06} or Microsoft Z3~\cite{DBLP:conf/tacas/MouraB08}.
